Cybersecurity Impacts of the Covid-19 Pandemic in Italy

### 2021-03-09 article.tex
Minor format change
Fixed police reference

The \textit{Digital Attacks Observatory} (OAD)~\cite{oadweb} is the only independent online survey in Italy about intentional digital attacks on IT systems of companies and public
bodies. It is implemented in collaboration with the Italian postal and telecommunication police.
The last OAD 2020 was the twelfth year of consecutive surveys on cyberattacks in Italy.
The OAD survey is not directed at a predefined set of respondents, but allows potential interested
parties to have full and free access to an online questionnaire, in a totally anonymous way.
The survey has collected responses from 310 enterprises in 2020, in comparison
to 296 and 2019 and 269 in 2018.
Thanks to the number of responses collected and their balanced distribution between companies and public bodies of different size and belonging to different economic
sectors, we can provide now a specific picture of the cyberattacks in Italy.

@@

\begin{figure}
	\centering
		\includegraphics[width=1\textwidth]{pictures/fig1.png}
		\caption{Extract of the OAD 2020~\cite{oad20} on the macro-evaluation
                  of the security level in the IT systems in Italy.
                  The chart shows that more than two thirds of the respondents
                  judge the level of cybersecurity of their IT systems as good.}
		\label{fig:1}
\end{figure}

@@

The impact of the pandemic on the cybersecurity in Italy is also highlighted by the data
provided by the postal and communication police, that shows the situation for the
critical infrastructures (Table~\ref{tab:table1}), for the financial cyber-crimes
(Table~\ref{tab:table2}) and for the cyber-terrorism (Table~\ref{tab:table3}). 
Fraudulent transactions in 2019 were blocked for a total value of \euro 21.3 million and \euro 18 million were recovered; in the first quarter of 
2020, fraudulent transactions for \euro 20.2 million were blocked,
practically reaching in four months the amount
blocked in the full twelve months of 2019, and \euro 8 million have been
recovered. This is an indication of the increase in attacks on financial transactions
and services due to the very large use of these online services, caused by the mobility reduction
measures consequent of the Covid-19 pandemic.

@@

	\caption{Data of critical structure protection collected by Italian postal and communication police~\cite{oad20}.}									
	\label{tab:table1}									
\end{table}

\begin{table}[h]
  \begin{center}
  \resizebox{1\textwidth}{!}{
	\begin{tabular}{|r|r|r|r|r|r|}									
		\hline									
		\textbf{Financial Cyber Crime}	&	1 Jan - 30 Apr	&	1 Jan - 31 Dec	&	1 Jan - 31 Dec &	1 Jan - 31 Dec &	1 Jan - 31 Dec\\
                	&	2020	&	2019	&	2018 &	2017 &	2016\\
		\hline									
		Blocked fraudulent transactions	&	\textbf{\euro 20.200.000,00}	&	\textbf{\euro 21.333.990,00}	&	\euro 38.400.000,00	& \euro 20.839.576,00 & \euro 16.050.812,50 	\\
		Recovered amounts 	&	\euro 8.700.000,00	&	\euro 18.000.000,00	&	\euro 9.000.000,00	&	\euro 862.000,00 & n.a.	\\
		People arrested	&	n.a.	&	n.a.	&	n.a.	&	25	& 25\\
		People reported	&	n.a.	&	n.a.	&	n.a.	&	2.851 & 3.772	\\
		\hline	
		Recovered amounts out of fraud	&	12,05\%	&	13,12\%	&	16,12\%	&	6,98\%	& 8,29\% \\
		\hline	
	\end{tabular}
	}
    \end{center}
	\caption{Data of critical structure protection collected by Italian postal and communication police~\cite{oad20}.}									
	\label{tab:table2}									
\end{table}

\begin{table}[h]
  \begin{center}
	\begin{tabular}{|r|r|r|r|}									
		\hline									
		\textbf{Cyber-terrorism}	&	1 Jan - 30 Apr 2020	&	1 Jan - 31 Dec 2019	&	1 Jan - 31 Dec 2018\\
		\hline									
		Monitored web space	&	\euro 11.962	&	\euro 36.377	&	\euro 36.000\\
		Removed contents 	&	n.a.\	&	n.a.\	&	250\\
		\hline	
	\end{tabular}
        \end{center}
	\caption{Data of cyber terrorism collected by Italian postal and communication Police~\cite{oad20}.}									
	\label{tab:table3}									
\end{table}

>>>>

The \textit{Digital Attacks Observatory} (OAD)~\cite{oadweb} is the only independent online survey in Italy about intentional digital attacks on IT systems of companies and public
bodies. It is implemented in collaboration with the Italian Postal and Telecommunication Police.
The last OAD 2020 was the twelfth year of consecutive surveys on cyberattacks in Italy.
The OAD survey is not directed at a predefined set of respondents, but allows potential interested
parties to have full and free access to an online questionnaire, in a totally anonymous way.
The survey has collected responses from 310 enterprises in 2020, in comparison
to 296 and 2019 and 269 in 2018.
Thanks to the number of responses collected and their balanced distribution between companies and public bodies of different size and belonging to different economic
sectors, we can provide now a specific picture of the cyberattacks in Italy.

@@

\begin{figure}
	\centering
		\includegraphics[width=0.9\textwidth]{pictures/fig1.png}
		\caption{Extract of the OAD 2020~\cite{oad20} on the macro-evaluation
                  of the security level in the IT systems in Italy.
                  The chart shows that more than two thirds of the respondents
                  judge the level of cybersecurity of their IT systems as good.}
		\label{fig:1}
\end{figure}

@@

The impact of the pandemic on the cybersecurity in Italy is also highlighted by the data
provided by the Italian Postal and Telecommunication Police, that shows the situation for the
critical infrastructures (Table~\ref{tab:table1}), for the financial cyber-crimes
(Table~\ref{tab:table2}) and for the cyber-terrorism (Table~\ref{tab:table3}). 
Fraudulent transactions in 2019 were blocked for a total value of \euro 21.3 million and \euro 18 million were recovered; in the first quarter of 
2020, fraudulent transactions for \euro 20.2 million were blocked,
practically reaching in four months the amount
blocked in the full twelve months of 2019, and \euro 8 million have been
recovered. This is an indication of the increase in attacks on financial transactions
and services due to the very large use of these online services, caused by the mobility reduction
measures consequent of the Covid-19 pandemic.

@@

	\caption{Data of critical structure protection collected by Italian Postal and Telecommunication Police~\cite{oad20}.}									
	\label{tab:table1}									
\end{table}

\begin{table}[h]
  \begin{center}
  \resizebox{1\textwidth}{!}{
	\begin{tabular}{|r|r|r|r|r|r|}									
		\hline									
		\textbf{Financial Cyber Crime}	&	1 Jan - 30 Apr	&	1 Jan - 31 Dec	&	1 Jan - 31 Dec &	1 Jan - 31 Dec &	1 Jan - 31 Dec\\
                	&	2020	&	2019	&	2018 &	2017 &	2016\\
		\hline									
		Blocked fraudulent transactions	&	\textbf{\euro 20.200.000,00}	&	\textbf{\euro 21.333.990,00}	&	\euro 38.400.000,00	& \euro 20.839.576,00 & \euro 16.050.812,50 	\\
		Recovered amounts 	&	\euro 8.700.000,00	&	\euro 18.000.000,00	&	\euro 9.000.000,00	&	\euro 862.000,00 & n.a.	\\
		People arrested	&	n.a.	&	n.a.	&	n.a.	&	25	& 25\\
		People reported	&	n.a.	&	n.a.	&	n.a.	&	2.851 & 3.772	\\
		\hline	
		Recovered amounts out of fraud	&	12,05\%	&	13,12\%	&	16,12\%	&	6,98\%	& 8,29\% \\
		\hline	
	\end{tabular}
	}
    \end{center}
	\caption{Data of critical structure protection collected by Italian Postal and Telecommunication Police~\cite{oad20}.}									
	\label{tab:table2}									
\end{table}

\begin{table}[h]
  \begin{center}
	\begin{tabular}{|r|r|r|r|}									
		\hline									
		\textbf{Cyber-terrorism}	&	1 Jan - 30 Apr 2020	&	1 Jan - 31 Dec 2019	&	1 Jan - 31 Dec 2018\\
		\hline									
		Monitored web space	&	\euro 11.962	&	\euro 36.377	&	\euro 36.000\\
		Removed contents 	&	n.a.\	&	n.a.\	&	250\\
		\hline	
	\end{tabular}
        \end{center}
	\caption{Data of cyber terrorism collected by Italian Postal and Telecommunication Police~\cite{oad20}.}									
	\label{tab:table3}									
\end{table}
